%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Documento LaTeX 																						%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Título:	Plantilla de PFC/TFG/TFM
% Autor:  Ignacio Moreno Doblas
% Fecha:  2014-02-01
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compilador: 	MiKTeX 2.9.
%	Modo:					PDFLaTeX.
% Entorno:			TeXnicCenter 2.0 Stable Beta 2.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Preámbulo del documento.
%-----------------------------------------------------------------%
% Clase de documento: libro
\documentclass[12pt,a4paper]{book} % article, report, book.

% Preámbulo: paquetes, comandos, entornos, estilos y título de página.
\input{A1.Preambulo.paquetes.tex}
\input{A2.Preambulo.commandos.tex}
\input{A3.Preambulo.entornos.tex}
\input{A4.Preambulo.estilodepagina.tex}

%Comando para crear glosario (index en inglés)
\makeindex


% Document body.
%-------------------------------------------------------------------%
\begin{document}

% Formato de documento hasta el capítulo 1 (sin incluirlo)
\frontmatter

%% Título y autor del proyecto
%%Rellenar con el nombre real del autor, título, tutor y año.
%%El departamento del tutor se escribe una vez en el Resumen del PFC
%\renewcommand{\pfcauthorname}{Nombre del autor}
%\renewcommand{\pfctitlename}{Título del proyecto}
%\renewcommand{\pfctutorname}{Nombre del tutor}
%\renewcommand{\pfcanno}{2014}

% Los tres ficheros siguientes solamente deben descomentarse
%  en el caso de ser un PFC del plan a extinguir.
% En los nuevos títulos de grado, no exiten la portada, la calificación 
%  ni el Resumen del PFC.
% Estos tres documentos deben tomarse de la web de la ETSIT.
%
% Portada.
%\input{B1.Portada.tex}

% Hoja de calificación
%\input{B2.Calificacion.tex}

% Resumen del proyecto (formulario)
%\input{B3.ResumenPFC.tex}

% Dedicatoria.
\input{B4.Dedicatoria.tex}

% Acrónimos
\input{B5.Acronimos.tex}

% Tabla de contenidos, figuras y tablas.
\input{B5.TableOfContents.tex}
\input{B5.TableOfFigures.tex}
\input{B5.TableOfTables.tex}

% Formato de documento durante los capítulos.
\mainmatter

% Prólogo.
\input{B6.Prologo.tex}

% Capitulos
\input{C1.Introduccion.tex}
\input{C2.Contexto.tex}
\input{C3.FudamentosTeoricos.tex}
\input{C4.TrabajoRealizado.tex}
\input{C5.Resultados.tex}
\input{C6.Conclusiones.tex}



%\input{D2.AppendixB.tex}

%\input{D3.AppendixC.tex}

% Formato de documento en la parte final.
\backmatter
%Hace que los capítulos y títulos nivel inferior no aparezcan numerados (lo que es ideal para conclusiones o notas finales).

% Bibliografía
%\input{E1.Bibliografia.tex}
%\input{Bibliografia_tres.tex}

\begin{thebibliography}{9}

\bibitem{Alzheimer1} 
	Henley, David B.,
	Sundell, Karen L.,
	Sethuraman, Gopalan,
 	Siemers, Eric R.,
	2011,	
	\textit{Safety profile of Alzheimer's disease populations in Alzheimer's Disease Neuroimaging 			Initiative and other 18-month studies},
 	407-416

\bibitem{ReservaCognitiva}
	Rodríguez Álvarez M., Sánchez J. L.,
	2004,
	\textit{Reserva cognitiva y demencia},
	2004, vol. 20, nº 2 (diciembre), 175-186 
	
\bibitem{DiagnosticoNormal}
 Petrella J.R, Coleman R.E., Doraiswamy P.M., Neuroimaging and Early Diagnosis
of Alzheimer Disease: A Look to the Future. Radiology 2003; 226:315?336.

\bibitem{MRIsurvey}
	Rémi Cuingnet et al, 
	\textit{Automatic classification of patients with Alzheimer's disease from
	structural MRI: A comparison of ten methods using the ADNI database},
	 Neuroimage,
	vol. 56, no. 2, pp. 766-781, 2011.

\bibitem{introPET}
	W. Cai, 
	D. Feng, 
	R. Fulton, 
	\textit{Content-based retrieval of dynamic PET functional images} 
	IEEE Trans. Inf. Technol. Biomed., vol. 4, no. 2, pp. 152-158, 2000.

\bibitem{PETMRIMultimodal}
	Ortiz, A.; 
	Fajardo, D.; 
	Górriz, J.M.; 
	Ramírez, J.; 
	Martínez-Murcia, F.J.,
	\textit{Multimodal
image data fusion for Alzheimer's Disease diagnosis by sparse representation}, 
International Conference on Innnovation in Medicine and Healthcare (InMed), 2014


\bibitem{PETMRIMultimodal2}
	Daoqiang Zhanga, 
	Yaping Wanga, 
	Luping Zhoua, 
	Hong Yuana, 
	Dinggang Shena,
	\textit{Multimodal Classification of Alzheimer's Disease and Mild Cognitive Impairment}
	Neuroimage. 2011 April 1; 55(3): 856-867


\bibitem{SVMtrees}
	D. Salas-Gonzalez, 
	J. M. Gorriz, 
	J. Ramírez, 
	M. Lopez, 
	I Alvarez,
	\textit{Compute-aided diagnosis of Alzheimer's disease using support vector machines and classification trees}
	Phys. Med. Biol. 55 (2010) 2807-2817


\bibitem{Survey}
	Ruaa Adeeb Abdulmunem Al-falluji
	\textit{MRI based Techniques for Detection of Alzheimer: A Survey}
	International Journal of Computer Applications (0975 - 8887)
	Volume 159 - No 5, February 2017

\bibitem{Survey2}
	S.Mareeswari1, 
	Dr.G.Wiselin,
	\textit{A survey Early Detection of Alzheimer's Disease using different techniques}
	International Journal on Computational Science and Applications (IJCSA) Vol.5, No.1,February 2015

\bibitem{CoD}
Bellman RE, 
1961,
\textit{Adaptive control processes: a guided tour}, Princeton
 University Press.


\bibitem{CoD2}
	David L. Donoho
	Department of Statistics
	\textit{High-Dimensional Data Analysis: The Curses and Blessings of Dimensionality}
	August 8, 2000

\bibitem{ReduceDimensionality}
	Benson Mwangi, 
	Tian Siva Tian,  
	Jair C. Soares
	\textit{A review of feature reduction techniques in neuroimaging}
	Neuroinformatics. 2014 April ; 12(2): 229-244. doi:10.1007/s12021-013-9204-3.

\bibitem{DeepLearning1}
	Siqi Liu, 
	Sidong Liu,
	\textit{EARLY DIAGNOSIS OF ALZHEIMER'S DISEASE WITH DEEP LEARNING}

\bibitem{DeepLearning2}
	Saman S., 
	Ghassem T.,
	\textit{Classification of Alzheimer's Disease Structural MRI Data by Deep Learning Convolutional Neural Networks}
	22 Jul 2016

\bibitem{AutoEncoderVariational}
	Diederik P. Kingma,
	Max Welling,
	\textit{Auto-Encoding Variational Bayes}
	1 May 2014

\bibitem{AutoEncoderOrigin1}
	 D. E. Rumelhart, G. E. Hinto, and R. J. Williams. 
	 Learning Internal Representations by Error Propagation
	 9 October 1986

\bibitem{AutoEncoderSurvey}
	: I. Guyon, 
	G. Dror, 
	V. Lemaire, 
	G. Taylor and 
	D. Silver
	Autoencoders, Unsupervised Learning, and Deep Architectures
	2012

\bibitem{AutoEncoderDenoising}
	P. Vincent
	H. Larochelle
	I. Lajoie
	Stacked Denoising Autoencoders: Learning Useful Representations in a Deep Network with a Local Denoising Criterion
	2010

\bibitem{DeepGenerativeModels}
	Danilo J. Rezende, 
	Shakir Mohamed, 
	Daan Wierstra
	Stochastic Backpropagation and Approximate Inference in Deep Generative Models

\bibitem{AD_historic}
	Bennett, D. A.,
	Evans, D. A., 
	1922.
	Alzheimer's Disease.
	Disease-a-Month 38(1), 7-64.

\bibitem{ADhistoric2}
	Nakako, S.,
	Kato, T.,
	Nakamura.,
	1996.
	Acetylcholinesterase activity in cerebrospinal fluid of patients with alzhimer's disease and senile dementia.
	Journal of the Neurological Sciences
	75(2).
\bibitem{mitocondria2}
	Rodriguez-Violante M.,
	Cervantes A.,
	Vargas S.,
	2010.
	Papel de la función mitocondrial en las enfermedades neurodegenerativas.
	Arch Neurocien (Mex)  Vol. 15, Nº1: 39-46

\bibitem{mitocondriaGeneral}
	Swerdlow, R.,
	2011
	Brain agin, alzheimer's diseas, and mitochondira.
	Biochim Biophys Acta 1812(12), 1630-1639


\bibitem{Nations}
	Nations U.,
	2008
	Department of economic and social affairs, world population prospects. 

\bibitem{Predemencia1}
	 Arnáiz E,., 
	 Almkvist O., 
	 2003,. 
	 Neuropsychological features of mild cognitive impairment and preclinical Alzheimer's disease. 



\bibitem{Predemencia2}
 	Palmer K., 
 	Berger A. K., 
 	Monastero R., 
 	Winblad B., 
 	Bäckman L., 
 	Fratiglioni L. 
 	2007. 
 	Predictors of progression from mild cognitive impairment to Alzheimer disease. 
 	Neurology 68 (19): 1596-1602. 
 	PMID 17485646. doi:10.1212/01.wnl.0000260968.92345.3f.

\bibitem{DemenciaMemoria}
	 Carlesimo GA, Oscar-Berman M (junio de 1992). «Memory deficits in Alzheimer's patients: a comprehensive review». Neuropsychol Rev 3 (2): 119-69. PMID 1300219.

 \bibitem{DemenciaComunicacion}
 	 Frank EM (septiembre de 1994). «Effect of Alzheimer's disease on communication function». J S C Med Assoc 90 (9): 417-23. PMID 7967534.
\bibitem{ADconducta}
	Volicer L, 
	Harper DG, 
	Manning BC, 
	Goldstein R, 
	Satlin A., 
	Mayo de 2001. 
	Sundowning and circadian rhythms in Alzheimer's disease». Am J Psychiatry 158 (5): 704-711. PMID 11329390. 


\bibitem{hipocampo}
	Mu Y., 
	Gage FH,
	2011 Dec,
Mol Neurodegener. 2011 Dec 22;6:85. doi: 10.1186/1750-1326-6-8
Adult hippocampal neurogenesis and its role in Alzheimer's disease.


\bibitem{atlasAlzheimer}
	FeldMan H. H.,
	Atlas of Alzheimer's Disease.
	Informa Healthcare

\bibitem{MainADNI}
	Susanne G. Mueller, 
	Michael W. Weiner, 
	Neuroimaging Clin N Am. 2005 November ; 15(4): 869?xii.
	The Alzheimer?s Disease Neuroimaging Initiative
	
\bibitem{}
 Gorji, H. T.; Haddadnia, J. (2015-10-01). "A novel method for early diagnosis of Alzheimer's disease based on pseudo Zernike moment from structural MRI". Neuroscience. 305: 361?371. ISSN 1873-7544. PMID 26265552. doi:10.1016/j.neuroscience.2015.08.013.

\bibitem{}
 Zhu, Xiaofeng; Suk, Heung-Il; Shen, Dinggang (2014-10-15). "A novel matrix-similarity based loss function for joint regression and classification in AD diagnosis". NeuroImage. 100: 91?105. ISSN 1095-9572. PMC 4138265?Freely 
 accessible. PMID 24911377. doi:10.1016/j.neuroimage.2014.05.078.

\bibitem{MRIOrigin3}
Wright G., 
Magnetic Resonance Imaging
EEE Signal Process. Mag. 14 (1997)56?66.


\bibitem{MRIOrigin}
Lauterbur P. C., 1973. 
"Image Formation by Induced Local Interactions: Examples of Employing Nuclear Magnetic Resonance". 
Nature. 242 (5394): 

\bibitem{MRIOrigin2}
 "Britain's brains produce first NMR scans". 
 New Scientist: 588. 1978.

\bibitem{MRINoise}
Snehal More, 
V.V.Hanchate,
"A Survey on Magnetic Resonance Image Denoising Methods"
International Research Journal of Engineering and Technology (IRJET),
Volume: 03 Issue: 05 | May-2016 

\bibitem{rbm}
Asja Fischer,
Christian Igel,
\textit{An Introduction to Restricted Boltzmann Machines}


\bibitem{denoising_autoencoder}
Vincent H.,
Larochelle H.,
Lajoie. I.,
\textit{Stacked Denoising Autoencoders: Learning Useful Representations in
a Deep Network with a Local Denoising Criterion}

\bibitem{denoising_autoencoder2}
Vincent, Pascal
Larochelle, Hugo
Bengio, Yoshua
\textit{Extracting and Composing Robust Features with Denoising Autoencoders},
  (ICML'08), pages 1096 - 1103, 2008

\bibitem{gan}
 Goodfellow, Ian J.; 
 Pouget-Abadie, Jean; 
 Mirza, Mehdi; 
 Xu, Bing; 
 Warde-Farley, 
 David; Ozair, 
 Sherjil; Courville, 
 Aaron; Bengio, Yoshua 
 (2014), 
 "Generative Adversarial Networks". arXiv:1406.2661?

\bibitem{gan_example}
Salimans T., 
Goodfellow I., 
Zaremba., 
Cheung, Vicki; Radford, Alec; Chen, Xi (2016).
"Improved Techniques for Training GANs". arXiv:1606.03498?



\bibitem{vae_2d}
Eunbyung Park 
University of North Carolina at Chapel Hill


\bibitem{mri_survey}
\textit{MRI based Techniques for Detection of Alzheimer: A
Survey} 
Ruaa Adeeb Abdulmunem Al-falluji
University of Babylon,
International Journal of Computer Applications (0975 ? 8887),
Volume 159 ? No 5, February 2017
\bibitem{ica}

Yang, Wenlu, et al. "Independent component analysis-
based classification of Alzheimer's disease MRI
data." Journal of Alzheimer's disease 24.4 (2011): 775-
783.

\bibitem{pca}
18F-FDG PET imaging analysis for computer aided
Alzheimer?s diagnosis? I.A. Illán, J.M. Górriz,J.
Ramírez, D. Salas-Gonzalez, M.M. López, F. Segovia,
R. Chaves, M. Gómez-Rio c, C.G. Puntonet,
Information Sciences 181 903?916, 2011.

\bibitem{wavelet}

Herrera, Luis Javier, et al. "Classification of MRI
Images for Alzheimer's Disease Detection." Social
Computing
(SocialCom),
2013
International
Conference on. IEEE, 2013.


\bibitem{knn}

Zhang, H., Berg, A.C., Maire, M., Svm-knn, J.M.:
Discriminative nearest neighbor classification for visual
category recognition. In: CVPR ?06, pp. 2126?2136.
IEEE Computer Society, Los Alamitos, CA, USA
(2006)

\bibitem{deep_learning}
Weiner, Michael (2017). "Recent publications from the Alzheimer's disease neuroimaging initiative: reviewing progress toward improved AD clinical trials.". Alzheimer's and dementia.


\bibitem{deep_learning_2}
 Suk, Heung-Il; Lee, Seong-Whan; Shen, Dinggang; Alzheimer?s Disease Neuroimaging Initiative (2016-06-01). 
 "Deep sparse multi-task learning for feature selection in Alzheimer's disease diagnosis". 

\bibitem{deep_learning_3}

 Zu, Chen; Jie, Biao; Liu, Mingxia; Chen, Songcan; Shen, Dinggang; Zhang, Daoqiang; Alzheimer?s Disease Neuroimaging Initiative (2016-12-01). "Label-aligned multi-task feature learning for multimodal classification of Alzheimer's disease and mild cognitive impairment". Brain Imaging and Behavior.

\bibitem{cnn_ad_1}
Hosseini-Asl E., 
Keynton R., 
El-Baz A.,
\textit{Alzheimer?s disease diagnostics by adaptation of 3d convolutional network}
(Julio 2016), 
arXiv:1607


\bibitem{cnn_ad_2}
Suk H-I., 
Shen D., 
\textit{Deep Learning-Based Feature Representation for AD/MCI Classification}, 
Medical image computing and computer-assisted intervention?(MICCAI), International Conference on Medical Image Computing and Computer-Assisted Intervention. 2013;16(0 2):583-590.

\bibitem{tensorflow}
Abadi M, 
Agarwal A., 
Barham P., 
B. Eugene,. 
\textit{TensorFlow:
Large-Scale Machine Learning on Heterogeneous Distributed Systems}, 
November 9, 2015

\bibitem{DNN_1}
D.E. Rumelhart, J.L. MacClelland (eds.) (1986). Parallel Distributed Processing.
Vol 1. Foundations, MIT Press

\bibitem{FA_1}
Glorot, X.,
Bengio, Y.,
(2010).
\textit{Understanding the difficulty of training deep feedforward neural networks}
Journal of Machine Learning Research - Proceedings Track. 9. 249-256.  

\bibitem{FA_2}
LeCun, Yann; Bengio, Yoshua; Hinton, Geoffrey (2015). "Deep learning". Nature. 521 (7553): 436?444. Bibcode:2015Natur.521..436L. PMID 26017442. doi:10.1038/nature14539.

\bibitem{DNN_training}
Xavier Glorot and Yoshua Bengio,
\textit{Understanding the difficulty of training deep feedforward neural networks},
(2010)
In Proceedings of the International Conference on Artificial Intelligence and Statistics (AISTATS?10). Society for Artificial Intelligence and Statistics

\bibitem{CNN}
LeCun,  Y.,  Boser,  B.,  Denker,  J.  S.,
Backpropagation  applied  to  handwritten  zip  code
recognition.
Neural Comput.
, 1(4):541?551, 1989

\bibitem{CNN_1}
Visualizing and Understanding Convolutional Networks
Ciresan, D. C., Meier, J., and Schmidhuber, J.  Multi-
column  deep  neural  networks  for  image  classifica-
tion.  In
CVPR
, 2012.

\bibitem{CNN_2}
Krizhevsky,  A.,  Sutskever,  I.,  and  Hinton,  G.E.   Im-
agenet classification with deep convolutional neural
networks.  In
NIPS
, 2012.

\bibitem{SVM_1}
Y. Zhang and W. Zhou, Multifractal analysis and
relevance vector machine-based automatic seizure
detection in intracranial, Int. J. Neural Syst. 25(6)
(2015) 1?14.

\bibitem{SVM_2}
E. Castillo, D. Peteiro-Barral, B. Guijarro Berdinas and O. Fontenla-Romero, Distributed one-class support vector machine, Int. J. Neural Syst. 25(7)
(2015) 1?17

\bibitem{SVM_3}
A. Hidalgo-Mun? noz, J. Górriz, J. Ramírez and
P. Padilla, Regions of interest computed by svm
wrapped method for Alzheimers disease examination
from segmented mri, Front. Aging Neurosci. 6(20)
(2014)

\bibitem{ValidacionCruzada}
Hatie T., Tibshirani R., Friedman J., The elements of statistical learning, data mining, inferencen, and prediction. Springer, 2008

\bibitem{AAL}
G. Flandin, F. Kherif, X. Pennec, D. Riviere,
N. Ayache and J.-B. Poline, fMRI data analysis, Proceedings of the IEEE Int. Symposium on Biomedical
Imaging (7?11 July 2002, Prague, Czech Republic),
pp. 907?910.

\bibitem{VBM}
Ashburner J., 
Friston KJ.
\textit{Voxel-based morphometry. The methods}
Neuroimage. 2000 Jun;11(6 Pt 1):805-21.

\bibitem{VBM_2}
J. Ashburner and T. Group, SPM8 Manuel, Vol. 12
(Functional Imaging Laboratory, Institute of Neurology, UK, 2011).


\bibitem{VBM_3}
Structural Brain Mapping Group, Department
of Psychiatry, Available at http://dbm.neuro.unijena.de/vbm8/VBM8-Manual.pdf [Accessed on 10
March 2014]

\bibitem{PET_norm}
N. S. V. Villemagne, 
S. Berlangieri, 
S. Lee, M. Cherk,
S. Gong, 
U. Ackermann, 
T. Saunder, 
H. TochonDanguy, G. Jones, C. Smith, G. OKeefe, C. Masters and C. Rowe, 
\textit{Visual assessment versus quantitative assessment of 11c-pib pet and 18f-fdg pet for
detection of Alzheimer?s disease}, J. Nucl. Med. 48(4)
(2004) 34?41.

\bibitem{Measures_1}
Wen Zhu, Nancy Zeng, Ning Wang. 
\textit{Sensitivity, Specificity, Accuracy, Associated
Confidence Interval and ROC Analysis with Practical SAS Implementations} 
1K\&L consulting services, Inc, Fort Washington, PA Octagon Research Solutions, Wayne, PA,
2010.

\bibitem{Measures_2}
Hwee Bee Wong, Gek Hsiang Lim. 
\textit{Measures of Diagnostic Accuracy: Sensitivity, Specificity, PPV and NPV} 
Health Services Research and Evaluation Division,
Ministry of Health, Singapore


\bibitem{learningRate}
Mandic, Danilo P. and Chambers, Jonathon A.
\textit{Towards the Optimal Learning Rate for Backpropagation}
2000,
01 Feb,
Neural Processing Letters

\bibitem{adam}
Diederik P. Kingma,
Jimmy Lei Ba. 
\textit{Adam: A method for stochastic Optimization} 
arXiv:1412.6980v9 [cs.LG] 30 Jan 2017


\bibitem{SGcomparativa}
Sebastian Ruder
\textit{An overview of gradient descent optimization
algorithms}
arXiv:1609.04747v2 [cs.LG] 15 Jun 2017


\end{thebibliography}



% Índice alfabético%
\input{F1.Index.tex}

\end{document}
